Disadvantage of procedural programming 
---------------------------------------
* Code is not reuseable
* Large Code base is hard to manage
* Difficult to tracking and fixing bug
* Data is Exposed to Whole programming
* Here Operations priority is higher than Data
* Difficult to relate with real world data 
-------------------------------------------
This problem solution is OOP 


-> What is OOP ?
  * OOP is a Object oriented programming

  --------****--------******------------

  1.Object oriented programming is all about objects.
  2.Class is a template to create multiple objects.


-----------------------------
  -> What is Class ?
    * Class is a data Shape.

  Class এর মধ্যে যা যা থাকে !
     1) Properties
     2) Privet Methods
     3) Public Methods



  -> What is Object?
     * Anything that needs multiple Attributes or multiple primitives to Define
     * Class is a blueprint to create multiple objects 
     * Object is king in object oriented programming


  Advantage in OOP
  ---------------------------------------------------
  * Combination of Noun, Adjective and Verb
  * A Capsule that can Encapsule Data and 
  * Has some privet and Public Properties
  * Has some function which is called Methods
  * Is a custom data type
  * A Isolated Environment for Properties and Methods
  ------------------------------------------------------


  OOP has Four main pillar

    1. Abstraction , 2. Encapsulation, 3. Inheritance, 4. Polymorphism


 -> What is Abstraction ?
    * Abstraction means Hiding the Implementation deal is inside and providing
      just the necessary API. we never know how it is working.we only know what 
      to do.
 
 -> What is Encapsulation ?
    * Same but some Different
    * Encapsulation means that each object in your code should control own state.
 
 -> What is Inheritance ?
    * it is used to define relationship between two class, 
      which a child class occurs all the properties and behaviours of a parent class. 
      Provides code reusability.

 -> What is Polymorphism ?
   * It is an ability of object to behave in multiple
     form. The most common use of polymorphism is Java, when a
     parent class reference type of variable is used to refer to a child
     class object.
     